---
title: "Analysing trends in Canadian glacers mass"
author: "Sergey Sidorov"
date: "11/18/2018"
output: 
  html_document:
    toc: yes
    toc_float: yes
    css: styles.css
  pdf_document:
    toc: yes
    keep_tex: yes
bibliography: bibl.bib
urlcolor: blue
params:
  filename: glacier.csv
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggvis)
options(scipen = 0, digits = 3)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

## Introduction

This is a first example of my tiny-investigation. The algorithm is taken from @SidorovAntonov_RandomCubatures. For more details of data you can find on <http://open.canada.ca/en/open-data>[^1].

[^1]: Here is the [direct link](https://github.com/tonytonov/Rcourse/blob/master/R markdown/demos/glacier.csv) to data download.

```{r, include=F}
glaicer <- read.csv(params$filename, na.strings = "..", comment.char = "#")
library(dplyr)
```

The data set contains `r nrow(glaicer)` measurments of `r nlevels(glaicer$GEO)` Canadian glaicer mass balance, collected `r min(glaicer$Ref_Date)` till `r max(glaicer$Ref_Date)`.

Namely, these file includes these glacers:

```{r}
levels(glaicer$GEO)
```

Among six investigated glaciers the most shorly history has `r glaicer %>%  group_by(GEO) %>% summarise(n = n()) %>%  arrange(n) %>% filter(row_number()==1) %>% select(GEO)`. 

Meanwhile median value measurments glacier near about zero namely `r glaicer %>%  group_by(GEO, MEASURE) %>% summarise(med = median(Value, na.rm = T)) %>% arrange(desc(med)) %>% head(1) %>% select(GEO)`. 

Just one NA value measurment has `r glaicer$GEO[is.na(glaicer$Value)]`.

## Hypotesis
We are interested in finding out wheter there is a stat.significant change in mass balance over the observed time period. For these purposes we use **R** version (`r getRversion()`) and an appropriate stat test called _t-test_: $$t = \frac{\overline{x} - mu_0}{s/\sqrt{n}}.$$

The workflow is as follows:

1. Read the file.
2. Run t-test for each glacier and collect p-values.
3. Support the evidence with 
    + a table of result;
    + a plot of could help demonstrate results.

## Analysis 
```{r analysis, cache=T}
glaicer <- glaicer %>% 
  select(Ref_Date, GEO, MEASURE, Value) %>% 
  filter(MEASURE == "Annual mass balance") %>% 
  separate(GEO, c("Name", "Location"), sep = " - ")

#descript analytics
g1 <- glaicer %>% 
  group_by(Name) %>% 
  summarise(YearsObserved = n(),
            MeanChange = mean(Value, na.rm = T),
            WorstChange = mean(Value, na.rm = T),
            WorstYear = Ref_Date[which.min(Value)])

#t-test
g2 <- glaicer %>% 
  group_by(Name) %>% 
  do({
    tt <- t.test(.$Value, alternative = "less", mu = 0, conf.level = .99)
    data.frame(PValue = tt$p.value, ConfidenceLimit = tt$conf.int[2])
  })

#group our computing into one table
left_join(g1, g2, by = "Name") %>% 
  knitr::kable(caption = "Descriptive stats and confidence intervals",
               digits = c(0,0,2,0,0,10,2)) #here we indicate, how much digits will be after dot
```

```{r ggplot, fig.width=10, fig.width=10}
#ggplot
# ggplot(glaicer, aes(Ref_Date, Value))+
#   geom_line()+
#   geom_hline(data = g1, aes(yintercept = MeanChange),
#              color = "red", linetype = "dashed", alpha = 0.9)+
#   facet_wrap(~ Name, nrow = 2)

ggvis(glaicer, ~Ref_Date, ~Value, stroke = ~Name) %>% 
  layer_lines()

```

The conductet analysis supports the evidence that Canadian glaicers are <u>melting</u>.

## Bibliography
